Ceph Parallel File System Evaluation Report

### 2013-10-02 ceph-tuning.tex
cutting

Deeper analysis with \verb!perf! showed that there was heavy lock contention
during parallel compaction in the Linux kernel memory manager.  This behavior
was first observed roughly in the kernel 3.5 time frame which was the kernel
installed on our test systems.\footnote{For more information,
please refer to \url{http://lwn.net/Articles/517082/} and
\url{https://patchwork.kernel.org/patch/1338691/}.}  We upgraded our test
systems with kernel version 3.9 and performed RADOS Bench test.  The results
were dramatic:  read performance improved from 4678 MB/s to 8643 MB/s (almost
an 85\% improvement).  Write performance was also fractionally improved from
4720 MB/s to 5284 MB/s 9an almost 12\% improvement).
%extremely positive and presented in
%Figure~\ref{fig:rados-kernel}. As can be seen, with the 3.9 kernel, while
%there was a slight improvement on write performance, read performance improved
%dramatically.  In addition to the kernel change, the amount of CephFS client
%kernel read-ahead cache size was increased as well.

@@

Additionally, we increased the size of the CephFS kernel client's read-ahead
chance.  IOR results reflecting the read-ahead cache size change are presented
in Figure~\ref{fig:ior-kernel-39}.

\begin{figure}[htb]
\centering
%\includegraphics[width=3.5in]{ior-kernel-39}
\includegraphics[width=3.5in]{ior_kernel_change}
\caption{CephFS performance with kernel changes to 3.9, IOR with 4 MB transfer
size}
\label{fig:ior-kernel-39}
\end{figure}

@@

\subsection{Metadata Performance Tuning}
For brevity's sake, we are omitting most of our file and directory creation
rate results.  However, over the course of our testing we did notice that in
CephFS 0.64 a significant improvement in the performance of file creation with
mdtest.  Shown in Figure~\ref{fig:mdtest-064-file-create}, we note
that as number of clients increase, the file creation rate does not scale
linearly, which suggested some form of lock contention.  Due to the large
differences in the initially observed performance, and the performance with
Ceph 0.64, opportunities for file and directory create tuning may be
substantial.

>>>>

Deeper analysis with \verb!perf! showed that there was heavy lock contention
during parallel compaction in the Linux kernel memory manager.  This behavior
was first observed roughly in the kernel 3.5 time frame which was the kernel
installed on our test systems.\footnote{For more information,
please refer to \url{http://lwn.net/Articles/517082/} and
\url{https://patchwork.kernel.org/patch/1338691/}.}  We upgraded our test
systems with kernel version 3.9 and performed RADOS Bench test.  The results
%were dramatic:  read performance improved from 4678 MB/s to 8643 MB/s (almost
were dramatic:  read performance improved from 4678 MB/s to 7499 MB/s 
(a 60\% improvement).  Write performance was also fractionally improved from
4720 MB/s to 5284 MB/s (a 12\% improvement).
%extremely positive and presented in
%Figure~\ref{fig:rados-kernel}. As can be seen, with the 3.9 kernel, while
%there was a slight improvement on write performance, read performance improved
%dramatically.  In addition to the kernel change, the amount of CephFS client
%kernel read-ahead cache size was increased as well.

@@

Additionally, we increased the size of the CephFS kernel client's read-ahead
chance.  
%IOR results reflecting the read-ahead cache size change are presented
%in Figure~\ref{fig:ior-kernel-39}.

\begin{comment}
\begin{figure}[htb]
\centering
%\includegraphics[width=3.5in]{ior-kernel-39}
\includegraphics[width=3.5in]{ior_kernel_change}
\caption{CephFS performance with kernel changes to 3.9, IOR with 4 MB transfer
size}
\label{fig:ior-kernel-39}
\end{figure}
\end{comment}

@@

\begin{comment}
\subsection{Metadata Performance Tuning}
For brevity's sake, we are omitting most of our file and directory creation
rate results.  However, over the course of our testing we did notice that in
CephFS 0.64 a significant improvement in the performance of file creation with
mdtest.  Shown in Figure~\ref{fig:mdtest-064-file-create}, we note
that as number of clients increase, the file creation rate does not scale
linearly, which suggested some form of lock contention.  Due to the large
differences in the initially observed performance, and the performance with
Ceph 0.64, opportunities for file and directory create tuning may be
substantial.
